Challenges and Solutions of Developing and Implementing a Revolutionary Novel Desktop-as-a-Service

### 2024-04-22 paper.tex
Some small fixes

The core component of DESIGN is our self-developed Web UI and the Control Application, that carries out the communication between all components of the service.

When starting an instance (virtual machine or container), they include a SSH service automatically. Our self-developed instance component waits until the SSH service is ready to satisfy requests in case applications are to be started or modifications are to be carried out, the instance component sends these requests to the virtual machine or container. Modification requests include resolution changes and fetching host status information.

In general, die self-developed instance component allows to carry out essential administration and usage tasks the operating systems does not offer via a generalized API.

TODO: Die letzten 3 Abschnitte noch überarbeiten und präzisieren

>>>>

The core components of DESIGN are our self-developed Web UI and the Control Application, which carry out the communication between all service components.

When starting an instance (virtual machine or container), it automatically includes an SSH service. Our self-developed instance component waits until the SSH service is ready to satisfy requests. In case applications are to be started or modifications are to be carried out, the instance component sends these requests to the virtual machine or container. Modification requests include resolution changes and fetching host status information.

In general, the self-developed instance component allows users to carry out essential administration and usage tasks that the operating system does not offer via a generalized API.

% TODO: Die letzten 3 Abschnitte noch überarbeiten und präzisieren
